 \documentclass{article}
\usepackage{ amsmath, amssymb, soul, color, amsthm}
\usepackage{mathtools}
\usepackage{tikz}
\usetikzlibrary{positioning}
\usepackage{soul, color}
\usepackage{ulem}
\usepackage[linguistics]{forest}

\title{STAT 451\_Hw 3}
\author{Julia Andrus}
\date{}

\begin{document}

\maketitle 

 7 : Ex 32, 38(b and c), 45, 47, 50, 52

\textbf{32)}





 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\textbf{38b)} Calculate 2 sided 95\% interval confidence interval for the true average work adhesion for UHPC adhered to steel. Does the interval suggest that 107 is a plausible value for the true average work for adhesion for UHPC adhered to steel. What about 110?


%%%%%%%%%%%%%%

\textbf{38b)} Predict the resulting work of adhesion value resulting from a single future replication of the experiment by calculating a 95\% prediction interval, and compare the
width of this interval to the width of the CI from (b).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\textbf{45)} Calculate a 99\% CI for the standard deviation of the coating layer thickness distribution. Is this interval valid whatever the nature of the distribution? Explain.

 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\textbf{47a)}  Estimate true average bond strength in a way that conveys information about precision and reliability.

%%%%%%%%%%%%%%
\textbf{47b)} Calculate a 95\% CI for the proportion of all such bonds whose strength values would exceed 10.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\textbf{50)} l of 99\% is more appropriate than the 95\% level used. What are the limits of the 99\% interval?


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\textbf{52)} a. Calculate and interpret a 95\% CI for true average arsenic concentration in all such water specimens.

%%%%%%%%%%%%%%
\textbf{52b)} Calculate a 90\% upper confidence bound for the standard deviation of the arsenic concentration distribution.


%%%%%%%%%%%%%%
\textbf{52c)} Predict the arsenic concentration for a single water specimen in a way that conveys information about precision and reliability.






\end{document}